Group meetings

### 2023-06-26 diapo/26-06-23_meeting/main.tex
Updated objectives

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{ c m{6cm} }
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task \cr
      0 & Work on thesis \\
      0.1 & Formula onChip Area \\
      1 & Find another LSTM problem \\
      2 & Try to reduce the scale factor again \\
      2.1 & Tensorflow custom function \\
    \end{tabular}
  \end{frame}

>>>>

    \centering
    \rowcolors{2}{evenRow}{oddRow}
    \begin{tabular}{ c m{6cm} }
      \rowcolor{firstRow}
      \color{white}\textbf{\#} & \centering\color{white}Task \cr
      0 & Work on thesis \\
      0.1 & Formula onChip Area \\
      0.2 & power consumption \\
      1 & Find another LSTM problem \\
      1.1 & Mbedded Video stabilization \\
      2 & Digital inference time \\
    \end{tabular}
  \end{frame}
